LSST Alerts: Science-Driven Options for Packets and their Distribution

### 2020-02-27 draft-alertcontents.tex
renamed files

@@

@@

\subsection{EM Counterparts to GW Events}\label{ssec:latency_emgw}
{\it Some contents revised from a Slack conversation between Federica Bianco, Om Sharan Salafia, and Eric Bellm.}

@@

@@

>>>>

\textcolor{red}{MLG notes from DESC: not all alerts need them so it could be, e.g., for new DIASources only, non-stellar DIASources, etc. with the rest going to a server that does not have the 1 minute latency requirements.}

@@

\textcolor{red}{MLG notes from DESC: \\ (1) Check "Host Galaxy Identification for Supernova Surveys" \citet{2016AJ....152..154G}. \\ (2) Alex Gagliano is working on host association as a part of classification that does a PCA on galaxy properties, and found that color and morphology are the first two PCA components, and that the hosts of SNIa SNII etc. occupy different parts of the PC2 vs PC1 plane. His paper is in prep still. \\ (3) As MWV was trying to tell you, host association depends on the redshift of the object (i.e., you want to do it in absolute distance); obviously that won't be in the alert so we can't make it part of the "3 nearest", but you'll probably want to mention that specifically.}.

@@

\subsection{EM Counterparts to GW Events}\label{ssec:latency_emgw}
{\it Some contents revised from a Slack conversation between Federica Bianco, Om Sharan Salafia, and Eric Bellm.} \textcolor{red}{MLG notes from DESC: the case for optical counterparts to neutrino events falls in this category as well, with perhaps the same challenge of them being not instantaneous so there is already some $>10$ minute delay such that 60s optical alerts from any follow-up aren't the bottleneck.}

@@

\citet{2018ApJ...854L..13H} searched for fast-fading transients in archival data from the intermediate Palomar Transient Factory (iPTF) and found 50 candidates, three of which were confirmed to be the afterglows of long GRBs. Of these three, two were in the archival data because the iPTF had done dedicated follow-up observations of Fermi detections, and one was serendipitous. They estimate an all-sky rate of such optical transients (peak $m<18$ mag, fade by at least 2 mag in 3 hours) of $680^{+2236}_{-119}$ events per year (similar to that of long GRBs). \textcolor{red}{MLG: still need some LSST projection here.}

@@

\citet{2006ApJ...644L..63K}, the discovery of three $<$hour optical transients in the Deep Lens Survey (one confirmed M star and two with potentially extragalactic origin), has been invoked as motivation for the 30 second exposure times and 60 second alert production latency -- e.g., the Deep Lens Survey is referenced without citation in the LSST Science Requirements Document. More recently, \citet{2013ApJ...779...18B} searched for fast optical transients in the Pan-STARRS1 Medium-Deep Survey identified 19 fast transients: 11 M dwarf flares and 8 likely solor system objects. \citet{2018ApJ...854L..13H} searched for fast-fading transients in archival data from the Palomar Transient Factor and found 50 candidates: three GRB afterglows (\S~\ref{ssec:latency_grb}), eight artifacts, one asteroid, and 38 with red stellar counterparts identified as M dwarfs. \textcolor{red}{Their Fig 1 is a delta-mag vs. delta-time plot comparing afterglows to Mdwarf flares that shows how they can be photometrically distinguished (difference regions of that parameter space)}. \textcolor{red}{Existence of short duration M dwarf flares established; what's the science related to them?}
